A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-03-28 README.Rmd
update of readme with the now available identifiers

---
output:
  md_document:
    variant: gfm
---

@@

<http://dx.doi.org/>…

@@

Not yet published.

@@

A Docker image is a lightweight GNU/Linux virtual computer that can be run as a piece of software on Windows, Linux, and OSX. To capture the complete computational environment used for this project we have a Dockerfile that specifies how to make the Docker image that we developed this project in. The Docker image includes all of the software dependencies needed to run the code in this project, including the data and code itself. To launch the Docker image for this project, first, [install Docker](https://docs.docker.com/installation/) on your computer and download the `.tar` file with the paper image [here](...) (not yet available). At the Docker prompt, you can load and run the image with:

@@

This will start a server instance of RStudio. Then open your web browser at localhost:8787 or run `docker-machine ip default` in the shell to find the correct IP address, and log in with rstudio/cultransbronze19. Once logged in, use the Files pane (bottom right) to navigate to the script files. More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

>>>>

---
output:
  md_document:
    variant: markdown
---

@@

<http://dx.doi.org/10.17605/OSF.IO/B6NP2>

@@

Not yet published: In review.

@@

A Docker image is a lightweight GNU/Linux virtual computer that can be run as a piece of software on Windows, Linux, and OSX. To capture the complete computational environment used for this project we have a Dockerfile that specifies how to make the Docker image that we developed this project in. The Docker image includes all of the software dependencies needed to run the code in this project, including the data and code itself. To launch the Docker image for this project, first, [install Docker](https://docs.docker.com/installation/) on your computer and download the `.tar` file with the paper image from the relevant repository (see DOI). At the Docker prompt, you can load and run the image with:

@@

This will start a server instance of RStudio. Then open your web browser at localhost:8787 or run `docker-machine ip default` in the shell to find the correct IP address, and log in with **rstudio/cultransbronze19**. Once logged in, use the Files pane (bottom right) to navigate to the script files. More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
